---
title: "Homework 6"
author: "Erfan Faridmoayer"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 50) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 50) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 



### Problem 2

```{r}
homocide_df = 
read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    resolved = ifelse(disposition == "Closed by arrest", 1, 0)
    ) %>%
  filter(!city_state == "Dallas, Tx", !city_state == "Phoenix, AZ", !city_state == "Kansas City, MO", !city_state == "Tulsa, AL", !victim_age == "Unknown") %>% 
    mutate(victim_age = as.numeric(victim_age)) %>% 
  filter(victim_race == c("Black", "White"))
```

In the code chunk above, I used the `homocide-data` database to create a dataframe, added the `city_state` variable, removed Tulsa, Kansas City, Phoenix, and Dallas using `filter()` function, created a new variable `solved` to post whether a case was solved or not, with 1 showing solved, and 0 showing not. The `victim_age` column was converted to numerical vector after tidy of unknown variables. Lastly, Black and White races were filtered.

```{r}
fit_logistic = 
  homocide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  mutate(victim_sex = fct_relevel(victim_sex, "Male")) %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial()) 
```

In the code chunk above, I filtered out Baltimore, MD from `city_state` variable. I then used the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim, age, sex, and race as predictors. The output of the model was saved as an object in `fit_logistic`. 

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>%
  mutate(
    ci_lower = exp(estimate-1.96*std.error),
    ci_upper = exp(estimate+1.96*std.error)
  ) %>% 
  knitr::kable(digits = 3)
```

Above, I used the `broom::tidy` package to tidy the object, and obtained OR based on the estimate, as well as the confidence intervals. Based on the results, we can tell that female victims had a lower likelihood of having their case resolved compared to male victims when keeping all other variables fixed.

```{r}
city_glm =
homocide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),
    results = map(models, broom::tidy, conf.int = TRUE)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI = conf.high - conf.low) %>% 
  filter(term == "victim_sexMale") %>% 
  arrange(OR)

city_glm %>% 
  ggplot(aes(x = OR, y = CI, color = city_state)) +
  geom_point()
```

Based on the code chunk above, we used the `purrr::map` function to calculate the OR and CI based on the previous code chunk on the cities in the dataset. When organized by OR, we can see that Stockton, CA had the highest likelihood of having their case resolved if the victim was male, and New York, NY had the least likelihood of having the case resolved if the victim was male among those who identify as either black or white. Lastly, we used `ggplot()` to map out CI and OR among different cities, coding them by their color.

